\documentclass[11pt]{article}
\usepackage[top=2.1cm,bottom=2cm,left=2cm,right= 2cm]{geometry}
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{changepage}
\usepackage{lscape}
\usepackage{ulem}
\usepackage{multicol}
\usepackage{dashrule}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumerate}
\newcommand{\urlwofont}[1]{\urlstyle{same}\url{#1}}
\newcommand{\degree}{\ensuremath{^\circ}}
\newcommand{\hl}[1]{\textbf{\underline{#1}}}



\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\newenvironment{choices}{
\begin{enumerate}[(a)]
}{\end{enumerate}}

%\newcommand{\soln}[1]{\textcolor{MidnightBlue}{\textit{#1}}}	% delete #1 to get rid of solutions for handouts
\newcommand{\soln}[1]{ \vspace{1.35cm} }

%\newcommand{\solnMult}[1]{\textbf{\textcolor{MidnightBlue}{\textit{#1}}}}	% uncomment for solutions
\newcommand{\solnMult}[1]{ #1 }	% uncomment for handouts

%\newcommand{\pts}[1]{ \textbf{{\footnotesize \textcolor{black}{(#1)}}} }	% uncomment for handouts
\newcommand{\pts}[1]{ \textbf{{\footnotesize \textcolor{blue}{(#1)}}} }	% uncomment for handouts

\newcommand{\note}[1]{ \textbf{\textcolor{red}{[#1]}} }	% uncomment for handouts

\begin{document}


\enlargethispage{\baselineskip}

Spring 2021 \hfill Jingchen (Monika) Hu\\

\begin{center}
{\huge MATH 241 Chapter 1 Live Exercises}	\\
\end{center}
\vspace{0.5cm}

\begin{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \item How many different 4-digit pins? Each digit can either be a letter or a number.
   
    \item Number of permutations of the letters in the word ``Vassar"?
    
    \item Suppose you have 3 distinctive gifts to give to 8 friends. How many permutations of give gifting strategy do you have?
    
    \item Lining up 8 people / 4 married couples.
    
    \begin{enumerate}
    \item In how many ways can 4 married couples line up? 
    \item What if couples must stand together?
    \end{enumerate}

     \item How many distinct hands of ``four of a kind" (four of the five cards are of the same rank)?
     
     \item Among 4 married couples, we want to select a group of 3 people that is not allowed to contain a married couple. How many choices are there?
     
     \item How many subsets are there of the set $\{1, 2, \cdots, n\}$?
     
     \item {\bf Order matters or not?}
     
     	\begin{enumerate}
	\item Textbook Example 5b: Ten children are to be divided into an $A$ team and a $B$ team of 5 each. The $A$ team will play in one league and the $B$ team in another. How many different divisions are possible?
	
	\item Textbook Example 5c: In order to play a game of basketball, 10 children at a playground divide themselves into two teams of 5 each. How many different divisions are possible?
	\end{enumerate}
	
      \item In a well shuffled deck of 52 cards, how many ways can the 4 Aces to be together?

\end{enumerate}


\end{document} 