\documentclass[11pt]{article}
\usepackage[top=2.1cm,bottom=2cm,left=2cm,right= 2cm]{geometry}
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{changepage}
\usepackage{lscape}
\usepackage{ulem}
\usepackage{multicol}
\usepackage{dashrule}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumerate}
\newcommand{\urlwofont}[1]{\urlstyle{same}\url{#1}}
\newcommand{\degree}{\ensuremath{^\circ}}
\newcommand{\hl}[1]{\textbf{\underline{#1}}}



\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\newenvironment{choices}{
\begin{enumerate}[(a)]
}{\end{enumerate}}

%\newcommand{\soln}[1]{\textcolor{MidnightBlue}{\textit{#1}}}	% delete #1 to get rid of solutions for handouts
\newcommand{\soln}[1]{ \vspace{1.35cm} }

%\newcommand{\solnMult}[1]{\textbf{\textcolor{MidnightBlue}{\textit{#1}}}}	% uncomment for solutions
\newcommand{\solnMult}[1]{ #1 }	% uncomment for handouts

%\newcommand{\pts}[1]{ \textbf{{\footnotesize \textcolor{black}{(#1)}}} }	% uncomment for handouts
\newcommand{\pts}[1]{ \textbf{{\footnotesize \textcolor{blue}{(#1)}}} }	% uncomment for handouts

\newcommand{\note}[1]{ \textbf{\textcolor{red}{[#1]}} }	% uncomment for handouts

\begin{document}


\enlargethispage{\baselineskip}

Spring 2021 \hfill Jingchen (Monika) Hu\\

\begin{center}
{\huge MATH 241 Chapter 2 Live Exercises}	\\
\end{center}
\vspace{0.5cm}

\begin{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \item  Chapter 2 Problem 5 \\
    A system is composed of 5 components, each of which is either working or failed. Consider an experiment that consists of observing the status of each component, and let the outcome of the experiment be given by the vector $(x_1, x_2, x_3, x_4, x_5)$, where $x_i$ is equal to 1 if component $i$ is working and is equal to 0 if component $i$ is failed.
    
   	\begin{enumerate}
	\item How many outcomes are in the sample space of this experiment?
	\item Suppose that the system will work if components 1 and 2 are both working, or if components 3 and 4 are both working, or if components 1, 3, and 5 are all working. Let $W$ be the event that the system will work. Specify all the outcomes in $W$.
	\item Let $A$ be the event that components 4 and 5 are both failed. How many outcomes are contained in the event $A$?
	\item Write out all the outcomes in the event $A \cap W$.
	\end{enumerate}
  
    \item What is the probability of drawing a jack or a red card from a well shuffled full deck?
    
    \item Suppose that for a randomly selected student in a probability class,
\begin{itemize}
\item $P(\text{live Eastern Time Zone at home}) = 63\%$, $P(\text{senior}) = 41\%$, $P(\text{brown eye color}) = 55\%$.
\item $P(\text{live Eastern Time Zone at home and senior}) = 31\%$, \\
$P(\text{live Eastern Time Zone at home and brown eye color}) = 33\%$, \\
$P(\text{senior and brown eye color}) = 24\%$
\item $P(\text{live Eastern Time Zone at home and senior and brown eye color}) = 18\%$
\end{itemize}
Find the probability that a student is either live Eastern Time Zone at home, a senior or having brown eye color.

    \item Two fair four-sided dice are rolled. Two events:
\vspace{-0.4cm}
\begin{align*}
A & = \{ \text{sum of two rolls is 5} \}\\
B & = \{ \text{minimum roll is 2} \}
\end{align*}
\vspace{-0.8cm}
\begin{enumerate}
\item Compute $P(A)$ and $P(B)$
\item Compute $P(A \cup B)$
\end{enumerate}

    \item For a class of 30 students, (i.e. $n = 30$), $P(\text{no match}) = 29.4\%$.
What is the chance of at least a tie in birthdays among these 30 students?

    \item Randomly pair 4 keys \{a, b, c, d\} with 3 locks \{a, b, c\}. Compute $P(\text{at least one match})$.
    
    \item In the game of bridge, the entire deck of 52 cards is dealt out to 4 players. What is the probability that one of the players receives all face cards?
\end{enumerate}


\end{document} 