\documentclass[11pt]{article}
\usepackage[top=2.1cm,bottom=2cm,left=2cm,right= 2cm]{geometry}
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{changepage}
\usepackage{lscape}
\usepackage{ulem}
\usepackage{multicol}
\usepackage{dashrule}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumerate}
\newcommand{\urlwofont}[1]{\urlstyle{same}\url{#1}}
\newcommand{\degree}{\ensuremath{^\circ}}
\newcommand{\hl}[1]{\textbf{\underline{#1}}}



\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\newenvironment{choices}{
\begin{enumerate}[(a)]
}{\end{enumerate}}

%\newcommand{\soln}[1]{\textcolor{MidnightBlue}{\textit{#1}}}	% delete #1 to get rid of solutions for handouts
\newcommand{\soln}[1]{ \vspace{1.35cm} }

%\newcommand{\solnMult}[1]{\textbf{\textcolor{MidnightBlue}{\textit{#1}}}}	% uncomment for solutions
\newcommand{\solnMult}[1]{ #1 }	% uncomment for handouts

%\newcommand{\pts}[1]{ \textbf{{\footnotesize \textcolor{black}{(#1)}}} }	% uncomment for handouts
\newcommand{\pts}[1]{ \textbf{{\footnotesize \textcolor{blue}{(#1)}}} }	% uncomment for handouts

\newcommand{\note}[1]{ \textbf{\textcolor{red}{[#1]}} }	% uncomment for handouts

\begin{document}


\enlargethispage{\baselineskip}

Spring 2021 \hfill Jingchen (Monika) Hu\\

\begin{center}
{\huge MATH 241 Chapter 4 part 3 Live Exercises}	\\
\end{center}
\vspace{0.5cm}

\begin{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\item Find the probability that a randomly selected Vassar student has odd number of siblings, if the average number of siblings is 1.73.

\item If you buy a lottery ticket in 50 lotteries, in each of which your chance of winning a prize is 1 / 100, what is the (approximate) probability that you will win a prize 

\begin{enumerate}[(a)]
\item at least once?
\item exactly once? 
\item at least twice?
\end{enumerate}

\item $X \sim \text{P}(\lambda)$. Which is the following is FALSE?

\begin{enumerate}[(a)]
\item The mean and standard deviation of $X$ are different.
\item Pmf of $X$ can be a decreasing function.
\item $\lambda$ can only take values $0, 1, 2, \ldots$.
\item None of the above.
\end{enumerate}

\item $X$ denotes the number of times a die is rolled until 6 is obtained.
\begin{enumerate}
\item What are the odds we have to roll it 10 or more times?
\item How many times do we expect to roll?
\item Find $Var[X]$.
\end{enumerate}

\item Consider independent trials with success probability $p$. Let $q = 1-p$.
What's the probability of getting $r$ successes before $m$ failures?

\begin{enumerate}[(a)]
\item $p^{r-1} q^m$
\item ${r + m -1 \choose r-1}p^{r-1} q^m$
\item $\sum_{k = r}^{r + m} {k -1 \choose r-1}p^r q^{k - r}$
\item  $\sum_{k = r}^{r + m-1} {k -1 \choose r-1}p^r q^{k - r}$
\end{enumerate}

\end{enumerate}


\end{document} 