\documentclass[11pt]{article}
\usepackage[top=2.1cm,bottom=2cm,left=2cm,right= 2cm]{geometry}
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{changepage}
\usepackage{lscape}
\usepackage{ulem}
\usepackage{multicol}
\usepackage{dashrule}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumerate}
\newcommand{\urlwofont}[1]{\urlstyle{same}\url{#1}}
\newcommand{\degree}{\ensuremath{^\circ}}
\newcommand{\hl}[1]{\textbf{\underline{#1}}}



\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\newenvironment{choices}{
\begin{enumerate}[(a)]
}{\end{enumerate}}

%\newcommand{\soln}[1]{\textcolor{MidnightBlue}{\textit{#1}}}	% delete #1 to get rid of solutions for handouts
\newcommand{\soln}[1]{ \vspace{1.35cm} }

%\newcommand{\solnMult}[1]{\textbf{\textcolor{MidnightBlue}{\textit{#1}}}}	% uncomment for solutions
\newcommand{\solnMult}[1]{ #1 }	% uncomment for handouts

%\newcommand{\pts}[1]{ \textbf{{\footnotesize \textcolor{black}{(#1)}}} }	% uncomment for handouts
\newcommand{\pts}[1]{ \textbf{{\footnotesize \textcolor{blue}{(#1)}}} }	% uncomment for handouts

\newcommand{\note}[1]{ \textbf{\textcolor{red}{[#1]}} }	% uncomment for handouts

\begin{document}


\enlargethispage{\baselineskip}

Spring 2021 \hfill Jingchen (Monika) Hu\\

\begin{center}
{\huge MATH 241 Homework 11}	\\
Due: Sunday 5/16 11:59pm to Moodle
\end{center}
\vspace{0.5cm}

\begin{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \item
    Chapter 7 Problem 4
    
    If $X$ and $Y$ have joint density function 
    
     \begin{equation*}
    f_{X, Y}(x, y) =
    \begin{cases}
      1/y, & \text{if $0 < y < 1, 0 < x < y$} \\
      0, & \text{otherwise}
    \end{cases}
  \end{equation*}
  find
  
  \begin{itemize}
  \item[(a)] $E[XY]$
  \item[(b)] $E[X]$
  \item[(c)] $E[Y]$
  \end{itemize}
  
  
    \item
    Chapter 7 Problem 7
    
    Suppose that $A$ and $B$ each randomly and independently choose 3 of 10 objects. Find the expected number of objects
    
    \begin{itemize}
    \item[(a)] chosen by both $A$ and $B$;
    \item[(b)] not chosen by either $A$ or $B$;
    \item[(c)] chosen by exactly one of $A$ and $B$. 
    \end{itemize}

    \item
    Chapter 7 Problem 30
    
    If $X$ and $Y$ are independent, and identically distributed with mean $\mu$ and variance $\sigma^2$, find
    
    $$
    E[(X - Y)^2]
    $$

    \item
    Chapter 7 Problem 33
    
    If $E[X] = 1$ and $Var(X) = 5$, find
    
    \begin{itemize}
    \item[(a)] $E[(2 + X)^2]$;
    \item[(b)] $Var(4 + 3X)$.
    \end{itemize}

    \item
    Chapter 7 Problem 36
    
    Let $X$ be the number of 1's and $Y$ the number of 2's that occur in $n$ rolls of a fair die. Compute $Cov(X, Y)$.

    \item
    Chapter 7 Problem 38
    
    The random variables $X$ and $Y$ have a joint density function given by
    
     \begin{equation*}
    f(x, y) =
    \begin{cases}
      2 e^{-2x}/x, & 0 \leq x < \infty, 0 \leq y \leq x \\
      0, & \text{otherwise}
    \end{cases}
  \end{equation*}
  
  Compute $Cov(X, Y)$.

    \item
    Chapter 7 Problem 53
    
    A prisoner is trapped in a cell containing 3 doors. The first door leads to a tunnel that returns him to his cell after 2 days' travel. The second door leads to a tunnel that returns him to his cell after 4 days' travel. The third door leads to freedom after 1 day of travel. If it is assumed that the prisoner will always select doors 1, 2, and 3 with respective probabilities 0.5, 0.3, and 0.2, what is the expected number of days until the prisoner reaches freedom?

    \item
    Chapter 7 Problem 65
    
    The number of winter storms in a good year is a Poisson random variable with mean 3, whereas the number in a bad year is Poisson random variable with mean 5. If next year will be a good year with probability 0.4 or a bad year with probability 0.6, find the expected value and variance of the number of storms that will occur. 


%    \item Theoretical exercise 13

%    \item Theoretical exercise 20
%
%    \item Theoretical exercise 29
%


\end{itemize}


\vspace{12pt}

\underline{Optional: if you feel like more practice}\\
These will not be graded, but you are welcome to discuss these with me during the office hour.

\begin{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\item Textbook  Chapter 7 Problems: 6, 31, 37, 39, 45
\item Textbook  Chapter 7 Theoretical exercise: 13, 20, 29

\end{itemize}








\end{document} 